\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-21 coq-example.tex
comments

Then we provide an overridable predicate \mintinline{Coq}{alg_is_prog : strs -> Type}, decidable provided the inductive hypothesis and sound \& complete w.r.t. to the specification \mintinline{Coq}{alg_is_prog e  <-> is_prog e}. We require extension to take care of the soundness \& completeness and the conditional decidablity.

Among them, completeness \mintinline{Coq}{is_prog e -> alg_is_prog e} is the most challenging part. This is proved by recursion on the predicate "is_prog e", but most of the handler on "is_prog" will not be reused because \mintinline{Coq}{alg_is_prog e} is overriden during inheritance. Unlike completeness, other parts of the construction, including soundness and and conditional decidability can be reused easily.

>>>>

Then we provide an overridable predicate \mintinline{Coq}{alg_is_prog : strs -> Type},\YZ{Why does it need to be overridden?}
decidable provided the inductive hypothesis and sound \& complete w.r.t. to the specification \mintinline{Coq}{alg_is_prog e  <-> is_prog e}. We require extension to take care of the soundness \& completeness and the conditional decidablity.

Among them, completeness \mintinline{Coq}{is_prog e -> alg_is_prog e} is
the most challenging part. This is proved by recursion on the predicate
"is_prog e", but most of the handler on "is_prog" will not be reused
because \mintinline{Coq}{alg_is_prog e} is overriden during
inheritance.\YZ{
    If alg_is_prog e is overridden, then how can ANY handler be reused?
}
Unlike completeness, other parts of the construction, including
soundness and and conditional decidability can be reused easily.
\YZ{But is the reusability achieved through a derived family's reusing handlers in the base family? Doesn't sound like it because the induction seems to be on strs.}
